Context Inconsistency Management \\Using Partial Constraint Checking

### 2011-03-03 paper/paper.tex
add section about inconsistency resolution

\section{Partial Constraint Checking}
Constraint checking techniques have been extensively studied in software engineering. Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}. Context-aware applications require more efficient algorithms because they use a huge set of contexts wich can change very rapidly and frequently (in the range of miliseconds). An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}. One example of an inefficient approach is nonincremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies. An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set. But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree. Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets. Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cons_comp_tree}
  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
  \label{fig:cct}
\end{figure}
Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes. More specifically, when a branch is added, only the values for the new branch itself and for the nodes from the branch top to the tree root need to be calculated. When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.

@@

\section{Context Inconsistency Resolution}

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cir}
  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
  \label{fig:cir}
\end{figure}

>>>>

\section{Partial Constraint Checking}
Constraint checking techniques have been extensively studied in software engineering. Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}. Context-aware applications require more efficient algorithms because they use a huge set of contexts, wich can change very rapidly and frequently (in the range of miliseconds). An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}. One example of an inefficient approach is nonincremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies. An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set. But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}. Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets. Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cons_comp_tree}
  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
  \label{fig:cct}
\end{figure}
Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes. More specifically, when a branch is added, only the values for the new branch itself and for the nodes from the branch top to the tree root need to be calculated. When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.

@@

\section{Context Inconsistency Resolution}
Now that we have an efficient method for detecting inconsistencies the task of resolving the conflicts remains. As discussed above the strategies for conflict resolution in literature are not very suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}. What really is needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context. Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}. More specifically they propose an algorithm that for every conflict set retains the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}). 
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{cir}
  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
  \label{fig:cir}
\end{figure}
This is based on the assumption that contexts that are most stably perceived by a system are most likely to be correct. This assumption is applicable to most of the environments in which pervasive systems run and is applied in many domains as a domain specific approach~\cite{xu:2010:PCC}.
